|

### 2024-10-25 output/seminar-slideshow.qmd
Adjust item distances

# Generate data for simple and complex factorial structures
simple_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',    ITEM_BASE_LOADING,
  'I2',  'F1',    ITEM_BASE_LOADING + ITEM_DIST,
  'I3',  'F1',    ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I4',  'F2',    ITEM_BASE_LOADING,
  'I5',  'F2',    ITEM_BASE_LOADING + ITEM_DIST,
  'I6',  'F2',    ITEM_BASE_LOADING + 2 * ITEM_DIST
)
complex_item_loadings <- simple_item_loadings |> bind_rows(
  tibble(
    item    = 'I3',
    factor  = 'F2',
    loading = ITEM_BASE_LOADING - 2 * ITEM_DIST # Secondary loading smaller
  )
)

@@

::: column
```{r scatter-method-factor}
LIM_INF <- -1.8
LIM_SUP <-  1.8

method_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',     ITEM_BASE_LOADING,
  'I1',  'M1',     0,
  'I2',  'F1',     ITEM_BASE_LOADING + ITEM_DIST,
  'I2',  'M1',     0,
  'I3',  'F1',     ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I3',  'M1',     0,
  'I4',  'F1',    -ITEM_BASE_LOADING,
  'I4',  'M1',     ITEM_BASE_LOADING - 2 * ITEM_DIST,
  'I5',  'F1',     ITEM_BASE_LOADING + ITEM_DIST,
  'I5',  'M1',    -ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I6',  'F1',    -ITEM_BASE_LOADING - ITEM_DIST,
  'I6',  'M1',    -ITEM_BASE_LOADING + 2 * ITEM_DIST
)

>>>>

# Generate data for simple and complex factorial structures
simple_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',    ITEM_BASE_LOADING,
  'I2',  'F1',    ITEM_BASE_LOADING + ITEM_DIST,
  'I3',  'F1',    ITEM_BASE_LOADING + 3 * ITEM_DIST,
  'I4',  'F2',    ITEM_BASE_LOADING - ITEM_DIST,
  'I5',  'F2',    ITEM_BASE_LOADING + ITEM_DIST,
  'I6',  'F2',    ITEM_BASE_LOADING + 2 * ITEM_DIST
)
complex_item_loadings <- simple_item_loadings |> bind_rows(
  tibble(
    item    = 'I3',
    factor  = 'F2',
    loading = ITEM_BASE_LOADING - 2 * ITEM_DIST # Secondary loading smaller
  )
)

@@

::: column
```{r scatter-method-factor}
method_item_loadings <- tribble(
  ~item, ~factor, ~loading,
  'I1',  'F1',     ITEM_BASE_LOADING,
  'I1',  'M1',     0,
  'I2',  'F1',     ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I2',  'M1',     0,
  'I3',  'F1',     ITEM_BASE_LOADING + 3 * ITEM_DIST,
  'I3',  'M1',     0,
  'I4',  'F1',    -ITEM_BASE_LOADING,
  'I4',  'M1',     ITEM_BASE_LOADING - 2 * ITEM_DIST,
  'I5',  'F1',     ITEM_BASE_LOADING + ITEM_DIST,
  'I5',  'M1',    -ITEM_BASE_LOADING + 2 * ITEM_DIST,
  'I6',  'F1',    -ITEM_BASE_LOADING - ITEM_DIST,
  'I6',  'M1',    -ITEM_BASE_LOADING + 3 * ITEM_DIST
)
